---
title: "esm_206_lab_8"
author: "Lauren Harris"
date: "11/16/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

library(tidyverse)
library(modelsummary)
library(corrplot)
library(broom)
library(here)
```

### Read in slo_homes.csv data
```{r}
homes <- read_csv(here("slo_homes.csv"))
```

### Create a subset with 4 cities

Task: create a subset called homes_subset that only contains observations where the city is one of the following:
- San Luis Obispo
- Atascadero
- Arroyo Grande
- Santa-Maria Orcutt

```{r}
homes_subset <- homes %>% 
  filter(City %in% c("San Luis Obispo", "Atascadero", "Arroyo Grande", "Santa Maria-Orcutt"))

# unique(homes_subset$City)
```

### A little exploration

Task: using the subset you just created, create a summary table that has the mean and sd of home prices grouped by city and sale status

```{r, include = FALSE, eval = FALSE}
homes_subset %>% 
  group_by(City, Status) %>% 
  summarize(mean_price = mean(Price),
            sd_price = sd(Price),
            mean_sqft = mean(SqFt))
```

Task: explore the relationship between square footage and home price using a scatterplot and homes_subset
```{r}
ggplot(data = homes_subset, aes(x = SqFt, y = Price)) +
  geom_point(aes(color = City)) +
  labs(x = "Square footage", y = "Price ($)") +
  geom_smooth(method = "lm", color = "black")
```

### Try a few linear models

Use multiple linear regression to investigate relationships between several predictor variables and home price

Create 2 different permutations of this model

(lm1) Price ~ City, Bedrooms, Bathrooms, SqFt, Status
(lm2) Price ~ City, SqFt, Status
(lm3) Custom one
```{r}
lm1 <- lm(data = homes_subset, Price ~ City + Bedrooms + Bathrooms + SqFt + Status)
summary(lm1)
# if I wanted to set my reference level as SLO
# Use fct_relevel() to specify a new reference level
new_homes_subset <- homes_subset %>% 
  mutate(City = fct_relevel(City, "San Luis Obispo"))
# this will use SLO as the reference level
lm_slo <- lm(Price ~ City + SqFt, data = new_homes_subset)

lm2 <- lm(data = homes_subset, Price ~ City + SqFt + Status)
summary(lm2)

lm3 <- lm(data = homes_subset, Price ~ Bedrooms + City + Status)
summary(lm3)
```
 
### Explore correlations between quantitative variables

Task: make a subset called homes_quant starting from homes-subset that only contains the variables from Price through SqFt

```{r}
homes_quant <- homes_subset %>% 
  select(Price:SqFt)

homes_cor <- cor(homes_quant)
corrplot(homes_cor, method = "ellipse")
```

### Comapre AIC values
```{r}
AIC(lm1)
AIC(lm2)
```

### Use modelsummary() to retun multiple model outputs

```{r}
modelsummary(list(lm1, lm2, lm3))
```

### Check diagnostic plots for lm1
```{r}
plot(lm1)
```

### Use broom::augment() to return the predictions for wxisting observations
```{r}
home_predictions <- augment(lm1)

# make a histogram of the residuals from this model
ggplot(data = home_predictions, aes(x = .resid)) +
  geom_histogram()
```

# BRANCHES R COOL